---
title: "Project Proposal"
author: "ALL group member names here"
subtitle: "Due November 17 at 11:59pm"
format: pdf
---

#### Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
```

# Dataset 1 (top choice)

**Data source:** NFL Kaggle 2025 Dataset

**Brief description:** Summary of data
Here, you'll find a summary of each data set in the 2025 Data Bowl, a list of key variables to join on, and a description of each variable. The tracking data is provided by the NFL Next Gen Stats team. The columns labeled with a prefix of "pff_" are provided by Pro Football Focus.

**Research question 1:**

-   Outcome variable (include the name/description and type of variable): Question: Does the distance that a quarterback drops back after the snap affect the probability of a pass completion?

Outcome Variable: Pass Result (passResult) - This is a binary variable, with categories such as "Complete" (C) and "Incomplete" (I), indicating whether the pass was successfully completed.
Dataset(s): This question would use the Play Data to access pass results and Player Play Data to analyze quarterback dropback distances.
Reasoning: This question explores how a continuous variable (dropback distance) might influence the likelihood of a binary outcome (pass completion). By focusing on quarterback actions and pass outcomes, it could help understand optimal dropback strategies.

**Research question 2:**

-   Outcome variable (include the name/description and type of variable):
Question: Does the college a player attended have an effect on their win rate in the NFL?

Outcome Variable: Win Rate - This would be a continuous variable, calculated as the proportion of games won by each player throughout their career. Win rate can be calculated as:
 
Independent Variable: collegeName - This is a nominal variable, representing the college a player attended.

Dataset(s): We’d use Player Data to get the player’s college and Player Play Data to track wins and losses for each game. We can then aggregate the win/loss data across each player’s career to calculate their career win rate.

**Load the data and provide a `glimpse()`**:

```{r data-1, warning=FALSE}

```

**Exploratory Plots:**

```{r plots-1}

```

# Dataset 2

**Data source:**

**Brief description:**

**Research question 1:**

-   Outcome variable (include the name/description and type of variable):

**Research question 2:**

-   Outcome variable (include the name/description and type of variable):

**Load the data and provide a `glimpse()`**:

```{r data-2, warning=FALSE}

```

**Exploratory Plots:**

```{r plots-2}

```

# 

# Dataset 3 (optional)

**Data source:**

**Brief description:**

**Research question 1:**

-   Outcome variable (include the name/description and type of variable):

**Research question 2:**

-   Outcome variable (include the name/description and type of variable):

**Load the data and provide a `glimpse()`**:

```{r data-3, warning=FALSE}

```

**Exploratory Plots:**

```{r plots-3}

```

# 

# Team Charter

#### When will you meet as a team to work on the project components? Will these meetings be held in person or virtually?

#### What is your group policy on missing team meetings (e.g., how much advance notice should be provided)?

#### How will your team communicate (email, Slack, text messages)? What is your policy on appropriate response time (within a certain number of hours? Nights/weekends?)?

#### 
